% -- Encoding UTF-8 without BOM
% -- XeLaTeX => PDF (BIBER)

\documentclass[]{cv-style}          % Add 'print' as an option into the square bracket to remove colours from this template for printing. 
                                    % Add 'espanol' as an option into the square bracket to change the date format of the Last Updated Text

\sethyphenation[variant=british]{english}{} % Add words between the {} to avoid them to be cut 

\begin{document}

\header{Paweł}{Weber}           % Your name
\lastupdated

%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION  -- In the aside, each new line forces a line break
%----------------------------------------------------------------------------------------

\begin{aside}
%
\section{contact}
Siemianowicka 3/7
52-014 Wrocław
~
+48 793 567 045
~
pawelweber@yahoo.pl
%
\section{languages}
    \begin{itemize}
        \item[Polish] - native
        \item[English] - B2/C1
    \end{itemize}
%
\section{programming}
\begin{itemize}
    \item[{\color{red} $\varheartsuit$} Python] - advanced
    \item[Bash] - intermediate
    \item[ANSI C] - intermediate
    \item[\LaTeX{}] - intermediate
\end{itemize}
%
\section{skills}
\begin{itemize}
    \item[Agile] - advanced
    \item[Docker] - advanced
    \item[Git] - advanced
    \item[CI/CD] - intermediate
    \item[AWS] - intermediate
\end{itemize}
%
\end{aside}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{experience}

\begin{entrylist}
%------------------------------------------------
\entry
  {03.19--Now}
  {Thaumatec Sp. z o.o.}
  {Wrocław, Poland}
  {\jobtitle{Technical Product Owner}\\
  Technical product owner in biometric project for US client. As technical product owner my responsibilities are:
  \begin{itemize}
    \item backlog maintenance
    \item negotiate acceptance criteria with stakeholder
    \item negotiate acceptance criteria and description with development team
    \item performing process of accepting, reviewing and sizing new items for backlog
    \item help team to understand the product owners priorities
    \item help stakeholder to prioritize the product backlog
    \item manage Jira
  \end{itemize}}
%------------------------------------------------
\entry
  {03.15--Now}
  {Thaumatec Sp. z o.o.}
  {Wrocław, Poland}
  {\jobtitle{Software Engineer}\\
  As a Software Engineer I'm a member of development team working on biometric device for humans recognition. My duties in team:
  \begin{itemize}
    \item developing and maintenance of CI/CD
    \item developing Python code
    \item developing C/C++ code
  \end{itemize}}
%------------------------------------------------
\entry
  {12.17--02.19}
  {Thaumatec Sp. z o.o.}
  {Wrocław, Poland}
  {\jobtitle{Scrum Master}\\
  As Scrum Master I was a member of development team working on biometric device for humans recognition. My duties were:
  \begin{itemize}
    \item Performing \& managing scrum meetings
    \item Performing \& managing daily stand-ups
    \item Coaching development team members and product owners
    \item Monitoring sprint progress and reporting status to product owners
  \end{itemize}}
%------------------------------------------------
\entry
  {12.14--03.15}
  {Nokia Sp. z o.o.}
  {Wrocław, Poland}
  {\jobtitle{SCM Engineer}\\
  My duties as SCM Engineer were:
  \begin{itemize}
    \item Automate the process of compiling source code into binary code
    \item Automate the process of assembling of software package for software release
    \item Automate the process of assembling of other software artifacts
    \item Cooperation with system architects and other stakeholders involved in a project
  \end{itemize}}
%------------------------------------------------

\end{entrylist}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{education}

\begin{entrylist}
%------------------------------------------------
\entry
{2013--2014}
{M.Sc. {\normalfont Advanced Applied Electronics}}
{Wrocław University of Science and Technology}
{\vspace{-0.3cm}}
%------------------------------------------------
\entry
{2009--2013}
{B.Eng. {\normalfont in Computer Science}}
{Wrocław University of Science and Technology}
{\vspace{-0.3cm}}
%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	OTHER QUALIFICATIONS SECTION
%----------------------------------------------------------------------------------------

\section{other qualifications}

\begin{entrylist}
%------------------------------------------------
\entry
{2016}
{2 days Scrum master training with SCRUM DROID workshop}
{Agile force}
{\vspace{-0.3cm}}
%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

\section{interests}
  \vspace{-0.2cm}

\textbf{professional:} Agile, Scrum, FPGA, microcontrollers, Computer architecture \\  
\textbf{personal:} brewing, speedway, physics \& astronomy 

%----------------------------------------------------------------------------------------

\end{document}
